\Title

### 2016-02-24 manuscript/manuscript.tex
Put residuals histogram before seismic diff
In CRUST1 synthetic results figure.

Fig.~\ref{fig:simple-results} summarizes the inversion results.
Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
after cross-validation.
The recovered model is smooth, indicating that the cross-validation procedure
was effective at estimating an optimal regularization parameter.
Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
(Fig.~\ref{fig:simple-data}a) and the estimated Moho depth.
The differences appear to be semi-randomly distributed with a maximum
coinciding with a short-wavelength feature in the true model.
The maximum and minimum differences are approximately
2.19 and -2.13 km, respectively.
Fig.~\ref{fig:simple-results}c shows inversion residuals (difference between
the observed and predicted data), in mGal.
The largest residual (in absolute value) coincides with the largest difference
between the true model and the estimate.
The inversion residuals are normally distributed,
as shown in Fig.~\ref{fig:simple-results}d,
with 0.02 mGal mean and a standard deviation of 3.63 mGal.
The cross-validation curve in Fig.~\ref{fig:simple-results}e
shows a clear minimum MSE at $\mu = 0.00046$
(indicated by the red triangle).
Fig.~\ref{fig:simple-results}f shows the convergence of
the Gauss-Newton optimization in eight iterations.

@@

Fig.~\ref{fig:crust1-results}c shows the final solution after both
cross-validation procedures.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-crust1-results}
    \caption{
        Inversion results from the CRUST1.0 synthetic data.
        (a) Cross-validation curve used to determine
        the regularization parameter (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.0001$ (red triangle).
        (b) Cross-validation results used to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:msehyper}) in $km^2$.
        The minimum (red triangle) is found at $z_{ref} = 30\ km$
        and $\Delta\rho = 350\ kg/m^3$.
        (c) The estimated Moho depth.
        (d) Difference between the CRUST1.0 model depths
        (Fig.~\ref{fig:crust1-data}a)
        and the estimated depths.
        (e) Histogram of the differences shown in (d).
        (f) Histogram of the inversion residuals
        (observed minus predicted data).
        (g) The inversion residuals.
        (h) Difference between the synthetic seismic observations
        (Fig.~\ref{fig:crust1-data}c)
        and the estimated depths.
    }
    \label{fig:crust1-results}
\end{figure*}

>>>>

Fig.~\ref{fig:simple-results} summarizes the inversion results.
Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
after cross-validation.
The recovered model is smooth, indicating that the cross-validation procedure
was effective in estimating an optimal regularization parameter.
Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
(Fig.~\ref{fig:simple-data}a) and the estimated Moho depth.
The differences appear to be semi-randomly distributed with a maximum
coinciding with a short-wavelength feature in the true model.
The maximum and minimum differences are approximately
2.19 and -2.13 km, respectively.
Fig.~\ref{fig:simple-results}c shows inversion residuals (difference between
the observed and predicted data), in mGal.
The largest residual (in absolute value) coincides with the largest difference
between the true model and the estimate.
The inversion residuals are normally distributed,
as shown in Fig.~\ref{fig:simple-results}d,
with 0.02 mGal mean and a standard deviation of 3.63 mGal.
The cross-validation curve in Fig.~\ref{fig:simple-results}e
shows a clear minimum MSE at $\mu = 0.00046$
(indicated by the red triangle).
Fig.~\ref{fig:simple-results}f shows the convergence of
the Gauss-Newton optimization in eight iterations.

@@

Fig.~\ref{fig:crust1-results}c shows the final solution after both
cross-validation procedures.
The recovered model is smooth, indicating that the cross-validation procedure
was effective in estimating an optimal regularization parameter.
Fig.~\ref{fig:crust1-results}d shows the difference between
the true Moho depth shown in Fig.~\ref{fig:crust1-data}a
and the estimate.
The maximum and minimum differences are, respectively,
9.8 and -8.2 km.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-crust1-results}
    \caption{
        Inversion results from the CRUST1.0 synthetic data.
        (a) Cross-validation curve used to determine
        the regularization parameter (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.0001$ (red triangle).
        (b) Cross-validation results used to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:msehyper}) in $km^2$.
        The minimum (red triangle) is found at $z_{ref} = 30\ km$
        and $\Delta\rho = 350\ kg/m^3$.
        (c) The estimated Moho depth.
        (d) Difference between the CRUST1.0 model depths
        (Fig.~\ref{fig:crust1-data}a)
        and the estimated depths.
        (e) Histogram of the inversion residuals
        (observed minus predicted data).
        (f) Histogram of the differences between
        the synthetic seismic observations (Fig.~\ref{fig:crust1-data}c)
        and the estimated depths.
        (g) The inversion residuals.
        (h) Difference between the seismic and the estimated depths.
    }
    \label{fig:crust1-results}
\end{figure*}
